RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-02-25 main.tex
:construction: Update introduction

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{IEEEkeywords}
	Input distribution design, energy detection, \gls{sic}-free receiver, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
\end{IEEEkeywords}

@@

	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace \gls{ioe}.

@@

	% \begin{subsection}{Related Works}
	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
	However, the work assumed equal symbol period and perfect synchronization for primary and backscatter links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
		\item The spreading factor (i.e., backscatter symbol period over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
	However, it severely limits the backscatter throughput and requires more \gls{sic} per backscatter symbol.

@@

	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
	\gls{ris} can also be used as an index-modulated information source and prototypes are already available for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	However, those joint designs incur advanced hardware architecture and high optimization complexity.
	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	% \end{subsection}
	Those problems are addressed in this paper and the contributions are summarized below.

	% \begin{subsection}{Contributions}
	% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the nodes information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
	\emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter} where the message of one or more RIScatter nodes and a primary transmitter are sequentially decoded by a co-located receiver.
	% The reflection pattern is random with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}
	% The reflection pattern is a discrete random variable with probability mass function
	% (co-located or dispersed)
	Each reflection state simultaneously acts as information codeword and passive beamforming codeword.
	The reflection pattern of each node is randomly chosen with the guidance of reflection state distribution, which is designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
	% That is, each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
	% Since each reflection state simultaneously acts as information codeword and passive beamforming codeword (symbol-level passive precoding).
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of line-coded \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	% Joint and independent encoding are available when multiple RIScatter nodes are
	Multiple RIScatter nodes can be co-located with joint encoding or dispersed with independent encoding.
	% The reflection state is neither fully random (cf. \gls{bc}) nor fully deterministic (cf. \gls{ris}), but semi-random in reflection state distribution.
	% RIScatter exploits the transmitter-scatter-receiver path for simultaneous backscatter modulation and dynamic passive beamforming, and can smoothly transition in between under different \gls{qos}.
	% A comparison of RIScatter to \gls{bc} and \gls{ris} is summarized in Table~\ref{tb:scattering_applications}.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the cooperative receiver design and the backscatter input distribution design.
	% such a novel scatter protocol encounters two major challenges, namely the cooperative receiver design and the adaptive backscatter input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

	\emph{Second,} we address the first challenge and propose a practical receiver that accommodates the properties of active-passive coexisting networks.
	It semi-coherently decodes the backscatter information by energy detection, recovers the exact reflection pattern, and coherently decodes the primary link.
	% Double modulation enables symbol-level passive precoding such that the
	Once successfully decoded, the multiplicative backscatter interference can be modelled as dynamic passive beamforming (rather than being re-precoded and cancelled), and thus the energy detection becomes part of channel training.
	The proposed receiver significantly improves backscatter throughput since it is suitable for arbitrary input distribution and spreading factor.
	This is the first paper to consider practical backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.

	\emph{Third,} we address the second challenge by considering a specific scenario where multiple co-located/dispersed RIScatter nodes ride over an active point-to-point \gls{miso} transmission to perform backscatter modulation and dynamic passive beamforming towards a nearby user.
	For a given \gls{qos}, we first express the primary and total backscatter rates as functions of \emph{input distribution} at RIScatter nodes, \emph{active beamforming} at the \gls{ap}, and \emph{backscatter decision regions} at the user.
	Then, we characterize the achievable rate region by optimizing those variables under different \gls{qos}.
	Since the original problem is highly non-convex, we propose a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing sequential quantization methods for \gls{dmtc}.
	Uniquely, we account for \gls{csi}, \gls{qos}, and backscatter constellation in those optimizations, and the proposed backscatter input distribution design is applicable to more general scenarios.
	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.

@@

\begin{section}{Scattering Principles}
	\gls{rf} wave scattering and reflecting can be described by a unified model and realized by {variable-load antennas} or {programmable metamaterial} \cite{Liang2022}.
	An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
	Ideally, it reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
	In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
	The scattered signal can be decomposed into a {structural} mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
	For an antenna-based (resp. metamaterial-based) scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
	\gls{bc} employ scatter nodes as information sources that \emph{randomly switching} between different states.
	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
	In contrast, \gls{ris} employ reflect elements as channel adaptors that \emph{deterministically choosing} the reflection state based on \gls{csi}.
	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
	\begin{equation}
		\Gamma_m = \beta_m \exp(j \theta_m),
		\label{eq:passive_beamforming}
	\end{equation}
	where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
\end{section}

>>>>

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{IEEEkeywords}
	Input distribution design, energy detection, \gls{sic}-free receiver, symbol-level precoding, active-passive coexisting network, backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
\end{IEEEkeywords}

@@

	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.

@@

	% \begin{subsection}{Related Works}
	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
	However, the work assumed equal symbol period and perfect synchronization for primary and backscatter links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
		\item The spreading factor (i.e., backscatter symbol period over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
	However, it severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.

@@

	On the other hand, static \gls{ris} design with fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	It was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020} then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information since the reflection state at each time slot is known to the receiver.
	\gls{ris} can also be used as an index-modulated information source and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
	This inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	However, those joint designs incur advanced hardware architecture and high optimization complexity.
	Relevant literature also considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	% \end{subsection}
	Those problems are addressed in this paper and the contributions are summarized below.

	% \begin{subsection}{Contributions}
	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	% \emph{First,} we propose RIScatter as a novel scatter protocol that simultaneously modulates the node information and engineers the wireless channel via adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission and simultaneously modulate their information and engineer the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links and each reflection state simultaneously acts as information and passive beamforming codewords.
	The reflection pattern of each node is semi-randomly chosen with the guidance of input distribution as a joint function of the information source, \gls{csi}, and \gls{qos}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Joint and independent encoding are available when multiple RIScatter nodes are co-located and dispersed, respectively.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the practical receiver and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

	\emph{Second,} we address the first challenge and propose a practical receiver that semi-coherently decodes the backscatter information, recovers the reflection pattern, and coherently decodes the primary link.
	We consider backscatter energy detection and formulate a \gls{dmmac} over disjoint decision regions.
	Thanks to the double modulation and symbol-level passive precoding, the semi-coherent backscatter decoding also acts as part of channel training.
	Once the backscatter information is successfully decoded, its contribution can be modelled within composite channel as dynamic passive beamforming rather than re-precoded and cancelled.
	It requires only one energy comparison and re-encoding per backscatter symbol and is much efficient than conventional decoding based on \gls{sic} and \gls{mrc}.
	It is also suitable for arbitrary input distribution and spreading factor, which significantly improves backscatter throughput.
	This is the first paper to consider practical backscatter-primary decoding scheme to exploit dynamic passive beamforming at the co-located receiver.

	\emph{Third,} we address the second challenge and consider a single-user multi-node \gls{miso} scenario.
	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is optimized by \gls{pgd}, and the decision regions are refined by existing sequential quantizer for \gls{dmtc}.
	Uniquely, we consider \gls{csi}, \gls{qos}, and backscatter constellation in the optimization and the input distribution result is applicable to general detection schemes.
	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.

@@

\begin{section}{RIScatter}
	\begin{subsection}{Principles}
		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		An antenna scatterer first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		An ideal metamaterial scatterer reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift on top.
		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
		In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and an antenna mode component that depends on the impedance mismatch \cite{Hansen1989}.
		The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
		% A natural question is, is it possible to use a scatterer
		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				\label{fg:input_distribution}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				\label{fg:time_structure}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
				% RIScatter node transmit symbol \num{1}
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
			\label{fg:scatter_comparison}
			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
			% There are many ways to order
